---
title: "Drought Assessment - Spring 2017"
output: word_document
---

This is a summary of conditions evaluated in early March 2017. For watersheds with probability of drought warning flow > 35%, a detailed summary will be provided.  Including: 

* Retrieve property variables with varkey = 
* Current total mean daily SW withdrawal in watershed
* 7Q10 estimate in watershed, ALF estimate in watershed, 2002 mean daily flow in September
* Table of users in watershed,
* * current mean daily SW withdrawal
* * Known reservoir storage total by watershed

```{r include = FALSE, warning = FALSE}
library(knitr)
# install.packages('knitr')
# install.packages('rmarkdown')

uri <-'http://deq2.bse.vt.edu/files/drought/mllr_max_2021.csv'
data = read.csv(uri, header = TRUE, sep = ",")

library("hydrotools")
ds <- RomDataSource$new("http://deq2.bse.vt.edu/d.dh/")
ds$get_token()
dvar <- ds$get_vardef("drought_status_mllr")
dvals <- ds$get_props(list(varid=dvar$varid, limit=500))


l90vals <- ds$get_props(list(propname="l90_Qout", limit=500))

```



```{r echo = FALSE}
kable(data[1:10,], digits=2)
```

```{r echo = FALSE}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)
kable(summary(out)$coef, digits=2)
```

